---
title: "Impact of co-creation methods on user engagement in digital health tools"
author: "Vinayak Anand-Kumar"
date: "2023-02-01"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r package-doc, message=FALSE, echo=FALSE}
source("R/00_load_package.R")
source("R/01_load_data.R")
source("R/02_format_data.R")
source("R/02_join_data.R")
source("R/03_prepare_data.R")
source("R/04_derive_variables.R")
source("R/05_engagement_1_frequency.R")
source("R/05_engagement_2_intensity.R")
source("R/05_engagement_3_duration.R")
```

```{r external, include=FALSE}
knitr::read_chunk("R/00_load_package.R")
knitr::read_chunk("R/01_load_data.R")
knitr::read_chunk("R/02_format_data.R")
knitr::read_chunk("R/02_join_data.R")
knitr::read_chunk("R/03_prepare_data.R")
knitr::read_chunk("R/04_derive_variables.R")
knitr::read_chunk("R/05_engagement_1_frequency.R")
knitr::read_chunk("R/05_engagement_2_intensity.R")
knitr::read_chunk("R/05_engagement_3_duration.R")
```

## Preliminary results

## Executive Summary

Preliminary findings indicate that:  
  
  - There are differences in frequency of web-app use, indicating that users logged in more often to Version 2 compared to Version 1  
  - There are differences in the intensity of use, suggesting that users are engaging more with the content of Version 2 compared to Version 1  
  - There are no differences in the duration of web-app use across the two versions

## Frequency of use

### Visual exploration of data
```{r average-log-ins-plot, message=FALSE, echo=FALSE}
```

### Statistical test for significance

#### Number of log ins between Version 1 and Version 2
```{r log-ins-test, message=FALSE, echo=FALSE}
```

## Intensity of use

### Visual exploration of data
```{r pages-viewed-plot, message=FALSE, echo=FALSE}
```

```{r lessons-viewed-plot, message=FALSE, echo=FALSE}
```

```{r open-ended-items-plot, message=FALSE, echo=FALSE}
```

```{r action-plan-created-plot, message=FALSE, echo=FALSE}
```

### Statistical test for significance

#### Proportion of pages viewed between Version 1 and Version 2
```{r pages-viewed-test, message=FALSE, echo=FALSE}
```

#### Lessons completed between Version 1 and Version 2
```{r lessons-viewed-test, message=FALSE, echo=FALSE}
```

#### Proportion of open ended items completed between Version 1 and Version 2
```{r open-items-test, message=FALSE, echo=FALSE}
```

#### Action plans completed between Version 1 and Version 2
```{r action-plans-test, message=FALSE, echo=FALSE}
```

## Duration of use

### Visual exploration of data
```{r time-spent-per-visit, message=FALSE, echo=FALSE}
```

```{r days-between, message=FALSE, echo=FALSE}
```

### Statistical test for significance

#### Time spent per log in between Version 1 and Version 2
```{r time-spent-test, message=FALSE, echo=FALSE}
```

#### Days of use between Version 1 and Version 2
```{r days-between-test, message=FALSE, echo=FALSE}
```